Efficient implementation of kernel filtering

### 2007-06-29 article/Article.tex
a few enhancements in the articles
darcs-hash:20070629164845-2fc9d-233d0d9ff15091e9b5d9cb3d8048fc234c3903ac.gz

\section{ITK implementation}
The filters discusses in this article are contained in 3 packages --
{\em consolidatedMorphology}, {\em fastRankMean} and {\em
boxConvolution}. The most recent versions of these packages can be
obtained from {\bf http://voxel.jouy.inra.fr/darcsweb/}. All of the packages
include multithreaded filters and include many examples. Unless
indicated otherwise, all filters will behave basically the same way as
other kernel filters, requiring either a radius or a neighborhood to
be specified.

@@

\section{Performance}
\subsection{Morpholgy}
\begin{table}[htbp]
\centering
\begin{tabular}{cccc}
\hline
Radius & Histogram & vanHerk/Gil-Weman & Anchor \\
1    &   0.0295  & 0.0228  & 0.033 \\
2    &   0.0219  & 0.0126  & 0.0187 \\
3    &   0.028   & 0.0128  & 0.0167 \\
4    &   0.0339  & 0.0262  & 0.0379 \\ 
5    &   0.0403  & 0.0264  & 0.0363 \\
6    &   0.046   & 0.0265  & 0.038 \\
7    &   0.052   & 0.027   & 0.0343 \\
8    &   0.0637  & 0.0275  & 0.0344 \\
9    &   0.0665  & 0.0387  & 0.0599 \\
10   &   0.117   & 0.0641  & 0.142 \\
15   &   0.103   & 0.0385  & 0.0455 \\
20   &   0.133   & 0.0409  & 0.0445 \\
25   &   0.164   & 0.0399  & 0.044 \\
30   &   0.199   & 0.0403  & 0.0427 \\
40   &   0.263   & 0.0405  & 0.0425 \\
50   &   0.329   & 0.0403  & 0.043 \\
100  &   0.68    & 0.0404  &  0.0472 \\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for dilation by circles using histogram, and polygon approximation based implementations applied to the $256 \times 256$ cthead image on a 1.8GHz AMD Athlon, 512KB cache. The polygon approximations use the default number of lines (a maximum of 6 when radius is greater than 8.\label{tab:perfPoly}}
\end{table}

@@

>>>>

\section{ITK implementation}
The filters discusses in this article are contained in 3 packages --
{\em consolidatedMorphology}, {\em fastRankMean} and {\em
boxConvolution}. The most recent versions of these packages can be
obtained from \url{http://voxel.jouy.inra.fr/darcsweb/}\footnote{
The most recent versions can be obtained using darcs \cite{DarcsWebSite}
with the command {\em darcs get http://voxel.jouy.inra.fr/\\darcs/contrib-itk/package},
where {\em package} must be replace by {\em consolidatedMorphology},
{\em fastRankMean} or {\em boxConvolution}.}.
All of the packages
include multithreaded filters and include many examples and tests. Unless
indicated otherwise, all filters will behave basically the same way as
other kernel filters, requiring either a radius or a neighborhood to
be specified.

@@

\subsection{Extended languages support}

All the new filters provided are wrapped using WrapITK's external projects
\cite{WrapITK} and have been successfully tested with python.

\section{Performance}

All the execution times in this section are measured on a computer with four
Intel\textregistered Xeon\textregistered CPU cores at 2.33GHz with 4MB cache,
running CentOS 4.4 64 bits. Unless precised in the description, the tests are
forced to run on a single core.

\subsection{Morpholgy}
\begin{table}[htbp]
\centering
\begin{tabular}{cccc}
\hline
Radius & Histogram & vanHerk/Gil-Weman & Anchor \\
1    &   0.0295  & 0.0228  & 0.033 \\
2    &   0.0219  & 0.0126  & 0.0187 \\
3    &   0.028   & 0.0128  & 0.0167 \\
4    &   0.0339  & 0.0262  & 0.0379 \\ 
5    &   0.0403  & 0.0264  & 0.0363 \\
6    &   0.046   & 0.0265  & 0.038 \\
7    &   0.052   & 0.027   & 0.0343 \\
8    &   0.0637  & 0.0275  & 0.0344 \\
9    &   0.0665  & 0.0387  & 0.0599 \\
10   &   0.117   & 0.0641  & 0.142 \\
15   &   0.103   & 0.0385  & 0.0455 \\
20   &   0.133   & 0.0409  & 0.0445 \\
25   &   0.164   & 0.0399  & 0.044 \\
30   &   0.199   & 0.0403  & 0.0427 \\
40   &   0.263   & 0.0405  & 0.0425 \\
50   &   0.329   & 0.0403  & 0.043 \\
100  &   0.68    & 0.0404  &  0.0472 \\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for dilation by circles using histogram, and polygon approximation based implementations applied to the $256 \times 256$ cthead image on a 1.8GHz AMD Athlon, 512KB cache. The polygon approximations use the default number of lines (a maximum of 6 when radius is greater than 8.\label{tab:perfPoly}}
\end{table}

@@

All the kernel based filters in ITK would also benefit to hinerit a common
super class which manage the neighborhood size and/or the kernel, and which
provide the infrastructure for the separable operations.
